### 2022-11-11 Thesis/text/methoden.tex
Update to Collision Behavior

The software requirements that improve the robot's behavior are derived from the current limitations of the standard ROS and Navigation2 setup for mobile robots described in the previous section. The non-functional requirements are listed separately in table \ref{tab:nonfn_req}. The functional requirements and their acceptance criteria are listed in table \ref{tab:fn_req} on page \pageref{tab:fn_req}. Figure \ref{fig:use_case} on page \pageref{fig:use_case} depicts a Use-Case diagram with the functions needed to improve the system's autonomy and better contextualize the system's requirements.

\begin{table}[ht]
	\centering
	\caption{Non-Functional Requirements}
	\label{tab:nonfn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.11\textwidth} | m{0.14\textwidth}| m{0.1\textwidth} | m{0.7\textwidth} |} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description} \\ 
			\hline
			non$\_$freq1 & Single Point of Failure & High & The system does not have a single point of failure	When parts of the system fail, the system maintains operability to a degree. \\ 
			\hline
			non$\_$freq2 & Performance & High & The system's control loop guarantees fast reactions. The average frequency with which the system operates is higher than 100Hz (10ms). \\ 
			\hline
			non$\_$freq3 & Determinism & High & The outcome for a given set of inputs must be deterministic, meaning that the behavior is always executed similarly. \\
			\hline
			non$\_$freq4 & Deliberate & High & The robot can execute deliberative behaviors, meaning that behaviors new implemented behaviors go beyond reacting to sensor input and have a planning aspect. \\
			\hline
		\end{tabular}
	}
\end{table}

\begin{table}[ht]
	\centering
	\caption{Functional Requirements}
	\label{tab:fn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.95\textwidth}{!}{%
		\begin{tabular}{| m{0.08\textwidth} | m{0.15\textwidth}| m{0.09\textwidth} | m{0.60\textwidth}|} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description/Acceptance Criteria} \\ 
			\hline
			fn$\_$req1 & Sensor Failure & High & The system detects sensor failure. Ensure that the system can restart sensors and decrease the speed during the time the sensor delivers limited information. \\ 
			\hline
			fn$\_$req2 & Emergency Detection & High & The system detects emergency. Ensure that the system can detect when the continuation on the calculated path is no longer safe (sensor failures, blockage). \\
			\hline
			fn$\_$req3 & Emergency Stop & High & The system can initiate emergency stops. Ensure that the system can override all commands and stop in case an emergency is detected. \\
			\hline 	
			fn$\_$req4 & Override Navigation2 & High & The system can override navigation2. Ensure that the system's commands can always override the commands coming from navigation2. \\
			\hline
			fn$\_$req5 & Maintain operability & High & The robot executes commands as long as it is safe. Ensure that the robot keeps driving if it is safe even when system functions are not working correctly. \\
			\hline
			fn$\_$req6 & Recovery & High & The system can recover from crashes. Ensure that the system can successfully reach goals despite previous crashes.\\ 
			\hline 
			fn$\_$req7 & Control Path Planning & Medium & The system controls and rates the quality of the planned paths. \\
			\hline	
			fn$\_$req8 & Reset Goals & Medium & The system can reset and override goals set by the user so that the goal is reachable by planners. \\
			\hline
			fn$\_$req9 & Robot Range & Medium & Ensure that the robot will not run out of battery during navigation to a goal. \\	
			\hline
		\end{tabular}
	}
\end{table}

>>>>

The software requirements that improve the robot's behavior are derived from the current limitations of the standard ROS and Navigation2 setup for mobile robots described in the previous section. The non-functional requirements and descriptions are listed in table \ref{tab:nonfn_req}. The functional requirements and their acceptance criteria are listed afterwards in table \ref{tab:fn_req} on page \pageref{tab:fn_req}. Figure \ref{fig:use_case} on page \pageref{fig:use_case} depicts a Use-Case diagram with the functions needed to improve the system's autonomy and better contextualize the system's requirements.

\begin{table}[ht]
	\centering
	\caption{Non-Functional Requirements}
	\label{tab:nonfn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{ | m{0.11\textwidth} | m{0.14\textwidth}| m{0.1\textwidth} | m{0.7\textwidth} |} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description/Acceptance criteria} \\ 
			\hline
			non$\_$freq1 & Single Point of Failure & High & The system does not have a single point of failure	When parts of the system fail, the system maintains operability to a degree. \\ 
			\hline
			non$\_$freq2 & Performance & High & The system's control loop guarantees fast reactions. The average frequency with which the system operates is higher than 100Hz (10ms). \\ 
			\hline
			non$\_$freq3 & Determinism & High & The outcome for a given set of inputs must be deterministic, meaning that the behavior is always executed similarly. \\
			\hline
			non$\_$freq4 & Deliberate & High & The robot can execute deliberative behaviors, meaning that behaviors new implemented behaviors go beyond reacting to sensor input and have a planning aspect. \\
			\hline
		\end{tabular}
	}
\end{table}

\begin{table}[ht]
	\centering
	\caption{Functional Requirements}
	\label{tab:fn_req}
	\renewcommand{\arraystretch}{1.5}
	\resizebox{0.9\textwidth}{!}{%
		\begin{tabular}{| m{0.08\textwidth} | m{0.15\textwidth}| m{0.09\textwidth} | m{0.60\textwidth}|} 
			\hline
			\textbf{Nr.} & \textbf{Name} & \textbf{Priority} & \textbf{Description/Acceptance Criteria} \\ 
			\hline
			fn$\_$req1 & Sensor Failure & High & The system detects sensor failure. Ensure that the system can restart sensors and decrease the speed during the time the sensor delivers limited information. \\ 
			\hline
			fn$\_$req2 & Emergency Detection & High & The system detects emergency. Ensure that the system can detect when the continuation on the calculated path is no longer safe (sensor failures, blockage). \\
			\hline
			fn$\_$req3 & Emergency Stop & High & The system can initiate emergency stops. Ensure that the system can override all commands and stop in case an emergency is detected. \\
			\hline 	
			fn$\_$req4 & Override Navigation2 & High & The system can override navigation2. Ensure that the system's commands can always override the commands coming from navigation2. \\
			\hline
			fn$\_$req5 & Maintain operability & High & The robot executes commands as long as it is safe. Ensure that the robot keeps driving if it is safe even when system functions are not working correctly. \\
			\hline
			fn$\_$req6 & Recovery & High & The system can recover from crashes. Ensure that the system can successfully reach goals despite previous crashes.\\ 
			\hline 
			fn$\_$req7 & Control Path Planning & Medium & The system controls and rates the quality of the planned paths. \\
			\hline	
			fn$\_$req8 & Reset Goals & Medium & The system can reset and override goals set by the user so that the goal is reachable by planners. \\
			\hline
			fn$\_$req9 & Robot Range & Medium & Ensure that the robot will not run out of battery during navigation to a goal. \\	
			\hline
		\end{tabular}
	}
\end{table}
